\RequirePackage{iftex}
\ifPDFTeX
  \documentclass[11pt,a4paper]{article}
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage{CJKutf8}
\else
  \documentclass[11pt,a4paper]{ctexart}
\fi
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{float}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{caption}

\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}
\setlength{\parskip}{0.5em}
\setlength{\parindent}{2em}
\captionsetup{font=small}
\author{方皓天 \quad 袁子恒}

\ifPDFTeX
  \AtBeginDocument{\begin{CJK*}{UTF8}{gbsn}}
  \AtEndDocument{\end{CJK*}}
\fi

\title{基于 MSWC English 的英语词首浊辅音检测与频谱分析}
\date{2026年4月29日}

\begin{document}
\maketitle

\begin{abstract}
本文选择 VE216 Project Topic 2 的语音分析任务，研究英语词首浊辅音 /g/、/b/、/d/、/z/ 的频谱特征与自动检测。数据来自 MSWC English，只保留首字母属于 \texttt{g/b/d/z} 且首个非元音音素严格对应 \texttt{G/B/D/Z} 的单词。受 /z/ 类候选词数量限制，最终每类选取 75 个词，共 300 个词、6796 条语音。方法上，先给出基于短时 FFT 幅度谱和归一化相关的检测方案，再介绍利用 log-mel 表示、词首定位、正负模板和自相关改进的 AI 重做版，最后以 MLP 和 CNN 作为神经网络对照。
\end{abstract}

\input{sections/problem_definition_cn.tex}
\input{sections/literature_review_cn.tex}
\input{sections/data_reconstruction_cn.tex}
\input{sections/theory_and_course_method_cn.tex}
\input{sections/case_analysis_cn.tex}
\input{sections/experiments_cn.tex}
\input{sections/ai_baselines_cn.tex}
\input{sections/discussion_cn.tex}
\input{sections/conclusion_cn.tex}

\appendix
\input{sections/appendix_algorithms_cn.tex}

\begin{thebibliography}{99}
\bibitem{davis1980}
S. Davis and P. Mermelstein, ``Comparison of Parametric Representations for Monosyllabic Word Recognition in Continuously Spoken Sentences,'' \textit{IEEE Transactions on Acoustics, Speech, and Signal Processing}, 1980. \url{https://doi.org/10.1109/TASSP.1980.1163420}.

\bibitem{rabiner1989}
L. R. Rabiner, ``A Tutorial on Hidden Markov Models and Selected Applications in Speech Recognition,'' \textit{Proceedings of the IEEE}, 1989. \url{https://doi.org/10.1109/5.18626}.

\bibitem{wilkinson2002}
N. J. Wilkinson and M. J. Russell, ``Improved Phone Recognition on TIMIT Using Formant Frequency Data and Confidence Measures,'' in \textit{Proc. ICSLP 2002}. \url{https://www.isca-archive.org/icslp_2002/wilkinson02_icslp.html}.

\bibitem{mazumder2021mswc}
M. Mazumder \textit{et al.}, ``Multilingual Spoken Words Corpus,'' in \textit{Proc. NeurIPS Datasets and Benchmarks}, 2021. \url{https://datasets-benchmarks-proceedings.neurips.cc/paper/2021/hash/fe131d7f5a6b38b23cc967316c13dae2-Abstract-round2.html}.

\bibitem{chen2014kws}
G. Chen, C. Parada, and G. Heigold, ``Small-Footprint Keyword Spotting using Deep Neural Networks,'' in \textit{Proc. ICASSP 2014}. \url{https://research.google/pubs/small-footprint-keyword-spotting-using-deep-neural-networks/}.

\bibitem{sainath2015}
T. N. Sainath and C. Parada, ``Convolutional Neural Networks for Small-Footprint Keyword Spotting,'' in \textit{Proc. Interspeech 2015}. \url{https://research.google/pubs/convolutional-neural-networks-for-small-footprint-keyword-spotting/}.

\bibitem{warden2018}
P. Warden, ``Speech Commands: A Dataset for Limited-Vocabulary Speech Recognition,'' arXiv:1804.03209, 2018. \url{https://doi.org/10.48550/arXiv.1804.03209}.

\bibitem{berg2021}
M. Berg \textit{et al.}, ``Keyword Transformer: A Self-Attention Model for Keyword Spotting,'' arXiv:2104.00769, 2021.

\bibitem{baevski2020}
A. Baevski \textit{et al.}, ``wav2vec 2.0: A Framework for Self-Supervised Learning of Speech Representations,'' arXiv:2006.11477, 2020. \url{https://doi.org/10.48550/arXiv.2006.11477}.

\bibitem{hsu2021hubert}
W.-N. Hsu \textit{et al.}, ``HuBERT: Self-Supervised Speech Representation Learning by Masked Prediction of Hidden Units,'' arXiv:2106.07447, 2021.

\bibitem{chen2022wavlm}
S. Chen \textit{et al.}, ``WavLM: Large-Scale Self-Supervised Pre-Training for Full Stack Speech Processing,'' \textit{IEEE Journal of Selected Topics in Signal Processing}, 2022. \url{https://arxiv.org/abs/2110.13900}.

\bibitem{gao2023}
C. Gao \textit{et al.}, ``Self-Supervised Speech Representation Learning for Keyword-Spotting with Light-Weight Transformers,'' arXiv:2303.04255, 2023. \url{https://arxiv.org/abs/2303.04255}.

\bibitem{kim2025}
D. Kim and J. Hwang, ``Fully End-to-end Streaming Open-vocabulary Keyword Spotting with W-CTC Forced Alignment,'' in \textit{Proc. Interspeech 2025}. \url{https://www.isca-archive.org/interspeech_2025/kim25d_interspeech.html}.
\end{thebibliography}

\end{document}
