\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{array}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{float}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{caption}
\usepackage{microtype}

\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue}
\setlength{\parskip}{0.45em}
\setlength{\parindent}{1.5em}
\captionsetup{font=small}
\sloppy

\title{Detecting Initial /g/, /b/, /d/, and /z/ in MSWC English:\\
\large A Course-Constrained Spectral Template Method with Extended Baselines}
\author{Heng Qiao}
\date{April 29, 2026}

\begin{document}
\maketitle

\begin{abstract}
This report reformulates VE216 Project Topic 2 as a controlled initial-consonant detection problem. From MSWC English, the subset keeps only words whose first letter is \texttt{g}, \texttt{b}, \texttt{d}, or \texttt{z} and whose first non-vowel ARPABET phone is the matching consonant. The resulting corpus contains 60 words and 3000 utterances. The main method, \texttt{strict\_course\_fft}, uses short-time framing, FFT magnitude spectra, maximum-energy blocks, normalized correlation, and a sliding maximum score. It reaches 0.343 exact-match accuracy on the four-way test set. An extended template method, \texttt{course\_filterbank\_corr}, adds log-mel localization, positive-negative templates, and envelope autocorrelation, raising exact-match accuracy to 0.550. A feature MLP reaches 0.527, while a small CNN reaches 0.320. The results show that /z/ is the easiest class because its frication persists over time, while /g/ is the hardest because its burst is short and sensitive to alignment. The main value of the study is an interpretable signal-processing pipeline that makes the acoustic evidence visible before comparing stronger baselines.
\end{abstract}

\noindent\textbf{Keywords:} speech analysis; voiced consonants; short-time Fourier transform; template matching; keyword spotting; MSWC.

\input{sections/problem_definition_en.tex}
\input{sections/literature_review_en.tex}
\input{sections/data_reconstruction_en.tex}
\input{sections/theory_and_course_method_en.tex}
\input{sections/case_analysis_en.tex}
\input{sections/experiments_en.tex}
\input{sections/ai_baselines_en.tex}
\input{sections/discussion_en.tex}
\input{sections/conclusion_en.tex}

\appendix
\input{sections/appendix_algorithms_en.tex}

\begin{thebibliography}{99}
\bibitem{davis1980}
S. Davis and P. Mermelstein, ``Comparison of Parametric Representations for Monosyllabic Word Recognition in Continuously Spoken Sentences,'' \textit{IEEE Transactions on Acoustics, Speech, and Signal Processing}, 1980. \url{https://doi.org/10.1109/TASSP.1980.1163420}.

\bibitem{rabiner1989}
L. R. Rabiner, ``A Tutorial on Hidden Markov Models and Selected Applications in Speech Recognition,'' \textit{Proceedings of the IEEE}, 1989. \url{https://doi.org/10.1109/5.18626}.

\bibitem{wilkinson2002}
N. J. Wilkinson and M. J. Russell, ``Improved Phone Recognition on TIMIT Using Formant Frequency Data and Confidence Measures,'' in \textit{Proc. ICSLP 2002}. \url{https://www.isca-archive.org/icslp_2002/wilkinson02_icslp.html}.

\bibitem{chen2014kws}
G. Chen, C. Parada, and G. Heigold, ``Small-Footprint Keyword Spotting using Deep Neural Networks,'' in \textit{Proc. ICASSP 2014}. \url{https://research.google/pubs/small-footprint-keyword-spotting-using-deep-neural-networks/}.

\bibitem{sainath2015}
T. N. Sainath and C. Parada, ``Convolutional Neural Networks for Small-Footprint Keyword Spotting,'' in \textit{Proc. Interspeech 2015}. \url{https://research.google/pubs/convolutional-neural-networks-for-small-footprint-keyword-spotting/}.

\bibitem{warden2018}
P. Warden, ``Speech Commands: A Dataset for Limited-Vocabulary Speech Recognition,'' arXiv:1804.03209, 2018. \url{https://doi.org/10.48550/arXiv.1804.03209}.

\bibitem{berg2021}
M. Berg \textit{et al.}, ``Keyword Transformer: A Self-Attention Model for Keyword Spotting,'' arXiv:2104.00769, 2021.

\bibitem{baevski2020}
A. Baevski \textit{et al.}, ``wav2vec 2.0: A Framework for Self-Supervised Learning of Speech Representations,'' arXiv:2006.11477, 2020. \url{https://doi.org/10.48550/arXiv.2006.11477}.

\bibitem{hsu2021hubert}
W.-N. Hsu \textit{et al.}, ``HuBERT: Self-Supervised Speech Representation Learning by Masked Prediction of Hidden Units,'' arXiv:2106.07447, 2021.

\bibitem{chen2022wavlm}
S. Chen \textit{et al.}, ``WavLM: Large-Scale Self-Supervised Pre-Training for Full Stack Speech Processing,'' \textit{IEEE Journal of Selected Topics in Signal Processing}, 2022. \url{https://arxiv.org/abs/2110.13900}.

\bibitem{gao2023}
C. Gao \textit{et al.}, ``Self-Supervised Speech Representation Learning for Keyword-Spotting with Light-Weight Transformers,'' arXiv:2303.04255, 2023. \url{https://arxiv.org/abs/2303.04255}.

\bibitem{kim2025}
D. Kim and J. Hwang, ``Fully End-to-end Streaming Open-vocabulary Keyword Spotting with W-CTC Forced Alignment,'' in \textit{Proc. Interspeech 2025}. \url{https://www.isca-archive.org/interspeech_2025/kim25d_interspeech.html}.
\end{thebibliography}

\end{document}
