\section{Dataset Construction and Labeling Rules}

\subsection{Selection rule}

The subset used in this report follows one simple rule:
\begin{quote}
A word is kept if and only if its first letter is one of \texttt{g/b/d/z} and its first non-vowel phone in CMUdict or ARPABET is the matching consonant \texttt{G/B/D/Z}.
\end{quote}

This rule turns a spelling-based filter into a pronunciation-based filter. It removes words in which the target letter appears in the spelling but does not define the initial consonant. It also separates the location of the written letter from the true acoustic boundary of the initial sound.

A check of the original candidate pool shows that 100 words per class are not possible under this strict rule. If each word only needs at least one utterance in train, development, and test, the numbers of candidate words are 957 for /g/, 2073 for /b/, 1932 for /d/, and only 75 for /z/. The final dataset therefore uses 75 words per class, which is the largest balanced choice allowed by the /z/ class. During sampling, each word keeps at least one utterance in train, development, and test, and the number of utterances per word is capped at 40/5/5 so that the dataset does not concentrate too many samples on a small set of words. The four classes are then truncated to the same sample counts in train, development, and test.

\subsection{Dataset size}

\begin{table}[H]
    \centering
    \caption{Size statistics of the filtered initial voiced-consonant subset.}
    \label{tab:dataset}
    \begin{tabular}{lcccc}
        \toprule
        Class & Words & Train & Development & Test \\
        \midrule
        /g/ & 75 & 1311 & 194 & 194 \\
        /b/ & 75 & 1311 & 194 & 194 \\
        /d/ & 75 & 1311 & 194 & 194 \\
        /z/ & 75 & 1311 & 194 & 194 \\
        \midrule
        Total & 300 & 5244 & 776 & 776 \\
        \bottomrule
    \end{tabular}
\end{table}

The resulting subset is balanced both in the number of words per class and in the number of utterances per split. The test set contains 194 utterances for each class and 776 utterances in total. This design increases lexical coverage and makes the task closer to cross-word detection of initial voiced consonants rather than recognition of a few representative words.
