\section{Problem Definition, Experimental Setting, and Metrics}

Let $x_i[n]$ denote the $i$th waveform. All recordings are resampled to $16$ kHz and trimmed or padded to $1$ s. The label set is
\[
C=\{g,b,d,z\}, \qquad y_i\in\{0,1\}^{|C|}.
\]
The report studies whether /g/, /b/, /d/, or /z/ appears at the beginning of a word. For any class $c\in C$, the task can be read as a one-vs-rest detector that asks whether the word onset is $c$. Because the current dataset keeps only four target onset consonants and each utterance contains exactly one of them, these four detectors are mutually exclusive in the present setting, so the same problem can also be written as single-label four-class classification. When all four class scores are low, the interpretation is that the sample provides little support for any of the four onset hypotheses. In the closed-set test used here, however, every sample belongs to one class in $C$, so the final report uses exclusive decoding.

Under this setting, each method first outputs a score vector $s_i\in\mathbb{R}^{|C|}$ and then decodes it into a predicted label $\hat y_i$. Since every sample satisfies $\sum_c y_{i,c}=1$, the reported evaluation uses
\[
\hat c_i=\arg\max_{c\in C}s_{i,c},\qquad
\hat y_{i,c}=\mathbf{1}[c=\hat c_i].
\]
Per-class thresholds are still estimated on the development set so that each score $s_{i,c}$ also keeps a one-vs-rest interpretation, but all tables in the report use the single-label decoding above.

All methods use the same train/development/test split. The training set is used only to estimate templates or train model parameters. The development set is used only to choose hyperparameters, thresholds, and early stopping. The test set is used only for the final metrics. No manual phone segmentation is provided, so every method has to locate useful evidence near the beginning of the word from the whole-word recording.

\subsection{Evaluation metrics}

Let $N$ be the number of test samples and let $K=|C|$. Label-wise accuracy compares each class bit separately:
\[
\mathrm{LabelAcc}
=\frac{1}{NK}\sum_{i=1}^{N}\sum_{c\in C}\mathbf{1}[\hat y_{i,c}=y_{i,c}].
\]
This metric is equal to $1$ minus Hamming loss. Because it rewards both true positives and true negatives, its value is higher than exact-match accuracy in a single-label task.

Exact-match accuracy requires the whole label vector to be correct:
\[
\mathrm{ExactMatch}
=\frac{1}{N}\sum_{i=1}^{N}\mathbf{1}[\hat y_i=y_i].
\]
Under the one-hot label setting used here, this metric is the standard four-class accuracy and serves as the main metric in the report.

For each class $c$, precision, recall, and F1 are defined as
\[
P_c=\frac{TP_c}{TP_c+FP_c},\qquad
R_c=\frac{TP_c}{TP_c+FN_c},\qquad
F1_c=\frac{2P_cR_c}{P_c+R_c}.
\]
Macro-F1 is the average of the four class-level F1 scores:
\[
\mathrm{MacroF1}=\frac{1}{K}\sum_{c\in C}F1_c.
\]
It does not weight classes by sample count, so it shows clearly whether one of /g/, /b/, /d/, and /z/ is sacrificed.

Micro-F1 first pools all $TP$, $FP$, and $FN$ counts and then computes F1:
\[
\mathrm{MicroF1}
=\frac{2\sum_c TP_c}{2\sum_c TP_c+\sum_c FP_c+\sum_c FN_c}.
\]
Samples-F1 computes F1 for each sample and then averages over samples:
\[
\mathrm{SamplesF1}
=\frac{1}{N}\sum_{i=1}^{N}
\frac{2|Y_i\cap \hat Y_i|}{|Y_i|+|\hat Y_i|}.
\]
Because both the ground-truth label and the predicted label contain exactly one active class, micro-F1, samples-F1, and exact-match accuracy have the same numerical value here. These metrics are still reported so that label-wise accuracy, exact-match accuracy, and per-class F1 can be read together from the same set of results.

The report compares three groups of methods in sequence. It first introduces the short-time FFT template method. It then presents the AI-assisted reimplementation method, which uses a stronger spectral representation and a more local detection strategy. The MLP and CNN appear last as neural baselines so that the main line of the report remains focused on the acoustic evidence itself.
